Reproducible Workflow on a Public Cloud for Computational Fluid Dynamics

### 2019-03-25 tex/MesnardoBarba2019.tex
Add words about the three-dimensional wake

Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
We note the presence of a recirculation region behind the snake cylinder and the deformation of the von Karman street as the spanwise vortices are convected away from the body (Fig. \ref{fig:ux_uy_xz_plane_3d}).
Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional wake generated by the snake model.

>>>>

Fig. \ref{fig:wz_avg_3d} shows the instantaneous spanwise vorticity averaged along the $z$-direction after $80$ and $100$ time units.
Compared to the snapshots from the two-dimensional simulation, we observe that (1) free-shear layers roll up into vortices further away from the snake body and (2) the von Karman street exhibits a narrower wake.
We note the presence of an unsteady recirculation region just behind the snake cylinder and alternating regions of positive and negative cross-flow velocity showing the presence of von Karman vortices (Fig. \ref{fig:ux_uy_xz_plane_3d}).
Fig. \ref{fig:qcrit_wx_3d} shows the isosurfaces of the Q-criterion after $100$ time units and highlights the complexity of the three-dimensional turbulent wake generated by the snake model.
